---
title: "Health Mapping"
author: "Matt Bixley"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  pdf_document:
    dev: jpeg
    df_print: kable
    fig_caption: yes
    fig_height: 4
    fig_width: 7
    number_sections: yes
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE,dpi=600)
library(tidyverse)
library(kableExtra)
```

```{r readdata, cache = T, include = F}
hdat <- read_csv(file="data/nz-health-survey-2016-17-regional-update-dhb-prevalences.zip")
```

```{r}
hdat <- read_csv(file="data/nz-health-survey-2016-17-regional-update-dhb-prevalences.zip")
```


# Mapping New Zealand Health Data

Lets take some health data from the [Ministry of Health](https://minhealthnz.shinyapps.io/nz-health-survey-2014-17-regional-update/_w_ffcb33f6/#!/home) Shiny App. tidy it up and plot it onto a Regional Map of New Zealand. The health website is it's own shiny app and we could do a lot of things there, but comparisons aren't so easy.

This is a reasonable chunk of data, `r nrow(hdat)` lines with `r ncol(hdat)` columns with these headers   
***`r colnames(hdat)`***

```{r demographics}
hdat %>% count(.,population,Ethnicity) %>% 
  kable(caption="Demographics", booktabs = T) %>% kable_styling(latex_options = "striped")
```
  



```{r categories}
hdat %>% count(.,short.description) %>% 
  kable(caption="Categories and Counts", booktabs = T, longtable = T) %>% 
  kable_styling(latex_options = "striped", font_size = 7)
```


## Plot
lets make a super simple plot with something in the data
```{r ADHD}
hdat %>% filter(.,short.description == "ADHD", type == "STD", sex != "All") %>% 
  ggplot(., aes(Prevalence_Mean,region,col=sex)) + geom_point()
```

```{r vegies}
hdat %>% filter(.,short.description == "Vegetable intake", type == "STD", sex != "All") %>% 
  ggplot(., aes(Prevalence_Mean,region,col=sex)) + geom_point()
```

```{r arthritis}
hdat %>% filter(.,short.description == "Arthritis", type == "STD", sex == "All") %>% 
  ggplot(., aes(Prevalence_Mean,region,col=year)) + geom_point()
```

# References