---
title: "Health Mapping"
author: "Matt Bixley"
date: "19 March 2019"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r readdata, cache = T, include = F}
hdat <- read_csv(file="data/nz-health-survey-2016-17-regional-update-dhb-prevalences.zip")
```

## Mapping New Zealand Health Data

Lets take some health data from the [Ministry of Health](https://minhealthnz.shinyapps.io/nz-health-survey-2014-17-regional-update/_w_ffcb33f6/#!/home) Shiny App. tidy it up and plot it onto a Regional Map of New Zealand. The health website is it's own shiny app and we could do a lot of things there, but comparisons aren't so easy.



This is a reasonable chunk of data, `r nrow(hdat)` lines with `r ncol(hdat)` columns with these headers   
***`r colnames(hdat)`***

lets make a super simple plot with something in the data
```{r}
newdat <- hdat %>% filter(.,short.description == "ADHD", 
                          type == "STD", 
                          sex != "All")

ggplot(newdat, aes(Prevalence_Mean,region,col=sex)) + geom_point()
```

